%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  (Master student in Computer Science, actively looking for a full-time software engineer position)

\begin{document}

%----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}rr}
%   \textbf{{\LARGE Jun Hao}} & \small Email : \href{mailto:jun.hao@wsu.edu}{\small jun.hao@wsu.edu} & \small Mobile:
%   (206)-643-7281
% \end{tabular*} 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Jun Hao}} & \footnotesize Email : \href{mailto:jun.hao@wsu.edu}{jun.hao@wsu.edu}\\
  \small Master student in Computer Science, actively looking for a full-time software engineer position& \footnotesize Mobile : 206-643-7281 \\
\end{tabular*}



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Washington State University}{Vancouver, WA}
      {Master of Science in Computer Science}{Expected Sep 2020}
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Bachelor of Science in Electrical Engineering}{Sep 2012 - Dec 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Washington State University}{Vancouver, WA}
      {Research Assistant/Teaching Assistant}{Aug 2017 - May 2019}
      \resumeItemListStart
        \resumeItem{Network Visualization: }
          {Designed a network visualization algorithm based on Force-Directed Graph Layout by adding auxiliary community information as force weights in \textit{matplotlib} and \textit{D3.js.}}
          \resumeItem{}{Improved edge crossing and node distribution with simulated annealing for better interpretability of layout.}
          \resumeItem{Diffusion Analysis and Visualization: }
          {Developed a Twitter network analysis web app with network-based diffusion analysis with \textit{React}, \textit{Neo4j}, and \textit{Node.js}, which is capable of visualizing sentiment and topic contagion in static or evolving networks. }
      \resumeItemListEnd

    \resumeSubheading
      {El Cielo Technology}{Beijing, China}
      {Embedded Software Engineer Intern} {Apr 2017 - Jun 2017}
      \resumeItemListStart
        \resumeItem{Embedded Systems on STM32: }
          {Designed the printed circuit boards with \textit{STM32} F2 and F4 chips and implemented embedded systems for controlling movement of antenna array, pre-processing and storing high-frequency incoming signals from antenna.}
          \resumeItem{}{Implemented APIs for upper level applications to access data in batches with Fourier transformation.}
        \resumeItem{}
          {Developed a web app as an internal supply chain data query platform in \textit{PHP and CSS} with \textit{Bootstrap.}}
      \resumeItemListEnd

    \resumeSubheading
      {DJI Technology Inc.}{Shenzhen, China}
      {Embedded Software Engineer Intern}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Computer Vision: }
          {Implemented a computer vision algorithm with ORB feature matching and mean shift tracking for object classification and viewpoint estimation in \textit{OpenCV-Python}.}
            \resumeItem{Flight Control for Drone Delivery: }
          {Designed and implemented an autonomous flight control system based on real-time feedback of a visual odometry and distance calibration with computer vision algorithm in \textit{C++} and \textit{Robot Operating System (ROS).}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  
   \resumeProheading{Multi-players Computer Game}{Vancouver, WA}
   \resumeItemListStart
    \resumeItem{Hollywood Hacker Game: }
      {Participated in the full Agile software development cycle of a real-time computer game for users to play mini-games in multiple threads from either hacker or security side.}
      \resumeItem{ }{Designed the multi-player game in an object-oriented application framework using \textit{Java} Slick2D.}
      \resumeItem{ }{Architectured the communication protocol based on TCP connection between multiple computers on LAN.}
    \resumeItemListEnd
    \resumeProheading{Minimum Distance Rumor Source Detection}{Vancouver, WA}
   \resumeItemListStart
    \resumeItem{Social Network Analysis: }
          {Simulated rumor backward propagation in a social network with SNAP library; implemented an algorithm based on maximum likelihood estimation and greedy search to select K candidates as rumor sources with the minimum total distance error in \textit{C++}}
          \resumeItem{}{\href{https://ieeexplore.ieee.org/document/8487400}{Published on the 27th International Conference on Computer Communications and Networks (ICCCN’18).}}
    \resumeItem{Spark: }{Designed and built data storage and processing with \textit{Scala} for high performance and scalability.}
    \resumeItemListEnd
    
    \resumeProheading{Parking Monitoring System for Capitol Hill Community}{Seattle, WA}
   \resumeItemListStart
    \resumeItem{Monitor Available Parking Space: }
          {Designed and developed a Python program to calculate the parking space in a garage; achieved 2\% error by monitoring cars in and out signals with data interrogating from RFID tags.}
          \resumeItem{}{Implemented a decision tree classifier to estimate occupation of individual parking spots with pictures from a low-resolution camera.}
          \resumeItem{}{Published data pipeline for API and visualization; deployed a web app with GoogleMaps iFrame on \textit{AWS}.}
    \resumeItemListEnd
    
%     \resumeProheading{Robomasters Robotics Competition}{Seattle, WA}
%   \resumeItemListStart
%     \resumeItem{Computer Vision and Control System}
%           {Programed a control system for a robot vehicle by C and applied YOLO on a real-time object detection program}
%     \resumeItemListEnd
    
    \resumeProheading{Network-based Interactive Game}{Seattle, WA}
  \resumeItemListStart
    \resumeItem{}
          {Built an asynchronous serial network system between two \textit{FPGA} boards by \textit{Verilog}; designed and implemented a 2-player Pokemon game in C under RS232 protocol on Nios II Microprocessor.}
    \resumeItemListEnd

    
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, C, Python, C++, JavaScript, PHP, CSS, Scala, Shell}
    %  \hfill
   }
   \vspace{-8 pt}
   \item{
   \textbf{Tools}{: Linux, OpenCV, Node.js, React.js, Tensorflow, scikit-learn, ROS, AWS, MySQL, Neo4j, Spark, Hadoop}
   }
 \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
